Variational Monte Carlo on bosonic systems

### 2018-01-25 project_1/article/article.tex
Add start of variable substitution
Add calculation of interaction functions

>>>>

            In order to derive the interaction functions we have to do a
            variable substitution. We replace the derivative of the radial
            component for particle $k$ by
                \tpl{{r_k}}
                = \dpd[]{r_{km}}{r_k}\tpl{{r_{km}}}.
            The derivative of the distance $r_{km}$ is given by
            \begin{gather}
                r_{km} = |r_k - r_m|
                \implies
                \dpd[]{r_{km}}{r_k}
                = \frac{r_k - r_m}{|r_k - r_m|}.
            \end{gather}
            Working in spherical coordinates we see that $u(r_{km})$ will only
            be a function of radii of particles $k$ and $m$. The gradient thus
            simplifies to the radial contribution giving
                \nabla_k u(r_{km})
                \vf{e}_{r}\tpl{{r_k}}u(r_{km})
                \vf{e}_r\dpd[]{r_{km}}{r_k}\tpl{{r_{km}}}u(r_{km})
                &= \vf{e}_r\frac{r_k - r_m}{r_{km}}
                \tpl{{r_{km}}}u(r_{km}).
            Using this expression we find the Laplacian to be
                \nabla_k^2 u(r_{km})
                \frac{1}{r_{km}} \tpl{{r_{km}}} u(r_{km})
                + \frac{(r_k - r_m)^2}{r_{km}^3} \tpl{{r_{km}}} u(r_{km})
                \frac{r_k - r_m}{r_{km}}\tpl{{r_{km}}}^2 u(r_{km})
